### 2015-02-11 README.Rmd
Attempted to fix plotless problem in rmd.

#We're clearly missing some interesting data, but we can still 
#perform some analysis.
data(safety)
```
```{r simpleplot}
plot_safety(first_qmj, safety)
```

```{r}
#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]
```
```{r simpleplot}
plot_quality(second_qmj, quality)
```

>>>>

#We're clearly missing some interesting data, but we can still 
#perform some analysis.
data(safety)
```
```{r fig.width=7, fig.width=6}
plot_safety(first_qmj, safety)
```

```{r}
#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]
```
```{r fig.width=7, fig.height=6}
library(ggplot2)
plot_quality(second_qmj, quality)
```
